---
title: "Assignment 4"
author: "Mike Lennon"
---


I used the algorithm that to be a best popular movie the rating has to be above 7.5
I then took the count of above average movies for each year
I also took the average rating of movies in that year.
In 2004 there was an 8.518 average movie rating
In 2004 there was also the highest total of hit movies. The total was 619 highly rated movies. I chose 2004 because the only other competitor that was close was 2005 and the number of hit  movies for 2005 was way smaller than for 2004


```{r include = FALSE}
#install.packages("ggplot2")
library(ggplot2)
library(plyr)



assign4 <- read.table("C:\\Users\\mike\\Desktop\\Data Aquisition\\movies.tab", 
                    sep="\t", header=TRUE, quote="", comment="")

goodMoviesOnly<- subset(assign4, rating > 7.5)
goodMoviesOnly1 <- goodMoviesOnly[order(goodMoviesOnly$year, goodMoviesOnly$rating),]
row.names(goodMoviesOnly1) <- NULL
goodMovieAvg <- aggregate(x=goodMoviesOnly1$rating,by=list(goodMoviesOnly1$year),FUN=mean)
 colnames(goodMovieAvg) <- c("year", "avgRating") #need to rename the cols of above 


meanVector <- colMeans(goodMovieAvg)
#Average rating was8.15

(meanMovieRating <- meanVector[2] )
#is.numeric(meanMovieRating)
#(meanMovieRating)


meanSD <- function(input){
  result <- data.frame(mean= apply(input,2,mean), stdDev = apply(input,2,sd))
  
  
}
(allStats <- alply(goodMovieAvg, 2,meanSD ))


columnOfOnes <- ifelse(goodMoviesOnly1$rating==1000,0,1)
goodMoviesOnly1$ones <- columnOfOnes

sumYears <- function(yearID){
  
  df<- goodMoviesOnly1[goodMoviesOnly1$year ==yearID,  ]
  return (sum(df$ones))
}

yearsUnique <- unique(goodMoviesOnly1$year)
str(yearsUnique)
yearCount <- sapply(yearsUnique, sumYears)
yearAndCount <- data.frame(yearsUnique,yearCount )



```
## Year and Average hit movie rating for that year

```{r}
(goodMovieAvg)
```



## Year and Hit Movie Count

```{r}
(yearAndCount)
```



## Supporting Graphs

**Here you can see the count of hit movies for each year plotted in a scatterplot. It is clear that the year 2004 has more hit movies ( as defined by a rating over 7.5) than any other year. **

```{r, echo=FALSE}

ggplot(yearAndCount, aes(x=yearsUnique, y= yearCount)) + geom_point()
```

**In this chart below, you can see that the year 2004 has the second highest average rating
of all of the years. It is second only to the year 2005 (8.586) and only by a small margin of .068. **


```{r, echo= FALSE}
ggplot(goodMovieAvg, aes(x=year, y= avgRating)) + geom_point()

```



